DATA 621 - Business Analytics and Data Mining

### 2020-11-20 HW5/HW5-Draft.Rmd
Too close to Shabbos, must stop.

A forward and backwards stepwise procedure based on AIC will be used, and the
model with the lowest AIC on the training set will be the selected to be tested
against the testing set. Using stepAIC precludes the use of k-fold cross
validation.

```{r m1TrainControl}
# All Modeler 1 models will use stepAIC so turn off cross-validation
trc <- trainControl(method = 'none')
```

### Poisson Model # 1

```{r m1PTrain}
set.seed(350047)
m1PFit <- train(TARGET ~ . + FreeSulfurDioxide:TotalSulfurDioxide +
                  AcidIndex * FixedAcidity * VolatileAcidity * pH +
                  Rated:STARS + LabelAppeal:Rated + LabelAppeal:Rated:STARS -
                  INDEX - STARS, data = m1trnXimp,
                trControl = trc, method = 'glmStepAIC',
                family = poisson(link = 'log'), direction = 'both', trace = 0)
# Save AIC
m1PFitAIC <- AIC(m1PFit$finalModel)
```

@@

### Negative Binomial Model # 1

### Multiple Linear Regrssion Model # 1

@@

## Multiple Linear Regrssion #2

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r targetH}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m1TrainControl}
```
```{r m1PTrain}
```
```{r m1PTable}
```
```{r m1PFitCheck}
```

>>>>

### Poisson Model # 1
For the Poisson model, a forward and backwards stepwise procedure based on AIC
will be used, and the model with the lowest AIC on the training set will be the
selected to be tested against the testing set. Using stepAIC precludes the use
of k-fold cross validation.

```{r m1PTrain}
# Using stepAIC so turn off cross-validation
trc <- trainControl(method = 'none')
set.seed(350047)
m1PFit <- train(TARGET ~ . + FreeSulfurDioxide:TotalSulfurDioxide +
                  AcidIndex * FixedAcidity * VolatileAcidity * pH +
                  Rated:STARS + LabelAppeal:Rated + LabelAppeal:Rated:STARS -
                  INDEX - STARS, data = m1trnXimp,
                trControl = trc, method = 'glmStepAIC',
                family = poisson(link = 'log'), direction = 'both', trace = 0)
# Save AIC
m1PFitAIC <- AIC(m1PFit$finalModel)
```

@@

### Negative Binomial Model # 1
```{r m1NBTrain, cache=TRUE}
glmc <- glm.control(maxit = 25, epsilon = 1e-12)
set.seed(72)
m1NBFit2a <- glm.nb(TARGET ~ . + FreeSulfurDioxide:TotalSulfurDioxide +
                      AcidIndex * FixedAcidity * VolatileAcidity * pH +
                      Rated:STARS + LabelAppeal:Rated +
                      LabelAppeal:Rated:STARS - INDEX - STARS,
                    data = m1trnXimp, control = glmc, link = log,
                    na.action = na.exclude)

m1NBFit2b <- stepAIC(m1NBFit2a, direction = 'both', trace = 1)

# Save AIC
m1NBFitAIC <- AIC(m1NBFit2b)
```

\small
```{r m1NBTable}
# Print results. This needed to ne in its own section so that the LaTeX commands
# to change the text size can be wrapped around it.
kable(summary(m1NBFit2b)$coefficients,
      caption = "Model 1 Negative Binomial Regression Output")
```
\normalsize

@@

## Multiple Linear Regrssion Model # 1

## Multiple Linear Regrssion Model # 2

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r statsN}
```
```{r graphsD}
```
```{r graphsH}
```
```{r corrgram}
```
```{r targetH}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1impute}
```
```{r m1postImputeD}
```
```{r m1postImputeH}
```
```{r m1PTrain}
```
```{r m1PTable}
```
```{r m1PFitCheck}
```
